An Open System for\\ Managing Short Programming Exercises

### 2013-08-08 paper/talk.tex
more tweaks

\begin{itemize}
  \item There are lots of programming exercise systems already:
  \begin{itemize}
    \item Free\footnote{As in beer}: CodingBat, Codecademy
    \item Commercial: CodeLab (TuringsCraft), MyProgrammingLab (Pearson)
    \item {\em Do we really need another one?}
  \end{itemize}
  \item We did not know of one that
  \begin{itemize}
    \item {\em Encouraged users to create and share exercises}
    \item Was open source
    \item Collected rich data about how students work
    \item Supported a range of languages (including C/C++)
  \end{itemize}
  \item We created a new system, called CloudCoder, to fill this niche
    \begin{itemize}
    \item \url{http://cloudcoder.org}
    \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item The impact of a pedagogical technique or curriculum material
        depends on how many students are exposed to it
  \item Systematically eliminating barriers to adoption maximizes impact
  \begin{itemize}
    \item Requiring payment is a barrier to adoption
    \item Restrictive licenses are a barrier to adoption
    \item Control by a central authority is a barrier to adoption
  \end{itemize}
  \item Ideal situation: resources are available to {\bf anyone} at {\bf any time} for {\bf any purpose}
%  \item Case in point...
\end{itemize}

>>>>

\begin{itemize}
  \item There are lots of programming exercise systems already:
  \begin{itemize}
    \item Free\footnote{As in beer}: CodingBat, Codecademy
    \item Commercial: CodeLab (TuringsCraft), MyProgrammingLab (Pearson)
    \item {\em Do we really need another one?}
  \end{itemize}
  \item We did not know of one that
  \begin{itemize}
    \item {\em Encouraged users to create and share exercises}
    \item Supported a range of languages (including C/C++)
    \item Was open source
    \item Collected rich data about how students work
  \end{itemize}
  \item We created a new system, called CloudCoder, to fill this niche
    \begin{itemize}
    \item \url{http://cloudcoder.org}
    \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item The impact of a pedagogical technique or curriculum material
        depends on how many students can access it
  \item Systematically eliminating barriers to adoption and distribution maximizes impact
  \begin{itemize}
    \item Requiring payment is a barrier
    \item Restrictive licenses are a barrier
    \item Control by a central authority is a barrier
  \end{itemize}
  \item Ideal situation: resources are available to {\bf anyone} at {\bf any time} for {\bf any purpose}
%  \item Case in point...
\end{itemize}
